---
title: "Meta-Analysis"
subtitle: "Frequentist Random Effects Results"
author: "Alan Ho"

abstract: Using Bayesian hierarchical (random effects) models for the meta-analysis with various priors for the heterogeneity parameter $\tau$, it was found that there was a significant treatment effect for depressive          symptoms (mean = 0.97, 95% CI ), anxiety (), and worry symptoms. However, there was substantial heterogeneity present specifically in the depressive symptoms subgroup where $tau$ was estimated to be between 0.58-1.12 where $\tau$ > 0.5 is considered substantial. In short, as with the frequentist meta-analysis results, the treatments did appear to have an effect but there is much uncertainty surrounding the treatment effect size though the 95% credible interval suggests that this effect might be at least what Cohen would indicate as medium (e.g. 0.39-0.41 found for Bayesian and Frequentist results), In terms of estimate shrinkage, there is Bevan et al. is most affected where their reweighted effect size is more than halved. 



output: pdf_document
header-includes:
    \usepackage{fancyhdr}
    \usepackage{float} 
    \usepackage{morefloats} 
    \floatplacement{figure}{h}
    \maxdeadcycles=200
    \usepackage{makeidx}
---

\newpage

\tableofcontents

\listoffigures
\listoftables

\newpage 

\addtolength{\headheight}{1.0cm} 
\pagestyle{fancyplain}
\rhead{\includegraphics[height=1.2cm]{C:/Users/uqaho4/Desktop/qbi_newcastle_logo.png}} 
\renewcommand{\headrulewidth}{0pt}


```{r, include=F}
setwd('..')
source('init.R')

knitr::opts_chunk$set(fig.pos = 'H')
```

# Statistical Analysis





# Results

```{r, echo=F, fig.cap='Treatment effects on Depressive/Anxious/Worry symptoms - Forest Plot', fig.height=4}
generate_forestplot(meta_results, perinatal_data)
```

\newpage

```{r, echo = F, message=F, warning=F}
knitr::kable(
  subgroup_analysis, 
  caption = 'Subgroup Analysis'
)

```


\newpage


## Depression

```{r, echo=F, fig.cap='Treatment effects on Depression - Forest Plot', fig.height=6}
generate_forestplot(meta_results, depression)
```

\newpage

## Anxiety 

```{r, echo=F, fig.cap='Treatment effects on Anxiety - Forest Plot', fig.height=6}
generate_forestplot(meta_results, anxiety)
```

\newpage

## Worry / Stress

```{r, echo=F, fig.cap='Treatment effects on Worry - Forest Plot', fig.height=6}
generate_forestplot(meta_results, worry)
```

\newpage


## Diagnostics


\newpage

1. Funnel Plots


```{r, echo = F, fig.cap = 'Funnel Plot (overall)'}
funnel(diagnostics(perinatal_data)$trim)
```

```{r, echo = F, fig.cap = 'Funnel Plot (Depression)'}
funnel(diagnostics(depression)$trim)
```

```{r, echo = F, fig.cap = 'Funnel Plot (Anxiety)'}
funnel(diagnostics(anxiety)$trim)
```

```{r, echo = F, fig.cap = 'Funnel Plot (Worry)'}
funnel(diagnostics(worry)$trim)
```

2. Normality Plots


3. Trim and fill 

```{r, echo = F}
knitr::kable(
  trim_fill.results,
  caption = "Trim and Fill Results"
)
```



4. Permutation and bootstrapping


# Conclusion






